---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# str.rdev

<!-- badges: start -->
[![R-CMD-check](https://github.com/StreamlineDataScience/str.rdev/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/StreamlineDataScience/str.rdev/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `str.rdev` is to download and process the Enron data set.

## Installation

You can install the development version of `str.rdev` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("StreamlineDataScience/str.rdev")
```

## Example

To download the data file:

```{r example, eval=FALSE}
library(str.rdev)

enron_download_data("path/ernron_raw_data.xls")
```

To process the XLS data:

```{r example2, eval=FALSE}

enron_process_data("path/ernron_raw_data.xls")
```


## Notes on implementation

The data processing function, `enron_process_data()` relies on known cells in 
the XLS spreadsheet. For example, the receipts data for the month of
December is stored in cells F72 to AJ84. If this were to change, the data 
processing would no longer work. Additionally, there is no way to know if the
rows/locations in each table (i.e. for each month) correspond to the
rows/locations listed in cells C4 to C16. The code assumes the order is the same 
for each month. If the collaborator sent a spreadsheet with data stored in 
different cells, the data processing function would need to be updated.


The Shiny app takes input from the user, the facility/location of interest, and
then creates a line plot of receipts over the time range. One basic 
improvement to the app is to add more reactivity to the plot, so that the user
can user their mouse to hover on the plot, and see the exact value (receipt
amount and date) for that observation. Another improvement is to add a plot for
deliveries, either in a separate tab or below the receipts plot. 



