---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# str.rdev

<!-- badges: start -->
[![R-CMD-check](https://github.com/StreamlineDataScience/str.rdev/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/StreamlineDataScience/str.rdev/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `str.rdev` is to download and process the Enron data set.

## Installation

You can install the development version of `str.rdev` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("StreamlineDataScience/str.rdev")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(str.rdev)
## basic example code
```

## Potential Issues
- Assumes headers will not change (i.e. Maximum, Avg) as grepl() is used to find and remove those columns. A different header will potentially break the code.
- Both functions assume the file downloads/saved with be an .xls; allowing for different file types could be a parameter
- enron_download_data() downloads data from the exact same link. Assumes data is on the first sheet.
- Assumes the date field will be an integer and exported using Excel's base date of Dec 30, 1899.

## Shiny app improvements
- Use golem package as it creates a Shiny app inside an R package architecture
- use shinydashboard + shinydashboardthemes + CSS to make app look less "out of the box"
- add company logo and use company colors
- Put plotly chart inside a module with parameters on which variables to plot
- separate app.R into ui and server
- Add total deliveries and receipts, and the difference and put all in value boxes
